\section{Conclusion}

Our purpose was to make a pilot-study for future development of V2X technology. We chose to create a database into which we parse information from a log-file given to us by Cybercom. This enables filtering and searching for specific data in the future development of the project. The next step of this project would be creating a program to visualise the data which would give a clearer understanding of what that data signifies. 
\paragraph{}
We were not able to simulate our hypothetical scenario because of the short time-span of the project and administrative issues (permits) with OsCar and OTTO, which was part of our original plan. But through our theoretical investigation and assumptions we can conclude that this is a promising project for students as a thesis work, since the concept behind V2X could be an implementable feature in upcoming projects. If we would to recommend this project as a thesis work for students, it would be necessary to have access to the software provided by Cybercom which is required to be able to test their theories in OsCar and OTTO. With the database that we created, it will be easier for future developers to understand the log-files and be able to read the information easier. With some modifications to the script you could visualise that information to help with building your own test scenarios. It would also be helpful to have a set Gantt-scheme to organise and structure the workload and set up smaller deadlines to test the implementations of V2X scenarios. 
 

