\section{Discussion}
For future work it is recommended to have documents, such as documentation about the project and NDA:s, prepared and ready for the first meeting with the assigned group and to have the software ready to be handed out. That would have helped the speed and progress of the project. Though, as mentioned before, with the circumstances that we had we think that our achievement is a good start for farther development of the V2X research. 
\paragraph{}
We chose not to create a test program based on out assumptions about the software without taking a look at it and without knowing its structure and what information we could receive. Instead we decided to focus on writing theoretically about the techniques of V2X and creating a database that simplifies the assessing of information from the log-file that we got from Cybercom and potentially easing the way for future developers to analyse this kind of information.

\paragraph{}
The time distribution was a problem mostly because it was very difficult for us to get the files and the program that we initially planned to work with. When we finally got the files that we needed there was little time left for us to analyse it and work on our scenario, which resulted in adding more limitations to our work, by scoping down to focusing on parsing the log file into a database. This caused our work to be very theoretical instead of being practical like we had planned from the start. We were anticipating from the start to have access to OTTO to be able to simulate a test to develop a basic implementation of our case scenario. Therefore, as we mentioned in the result, we were only able to create a database and construct a basic implementation which stores information from the log file in a database. 

\paragraph{}
The cooperation between all the group members in the project worked well and we did everything that we could to create something useful with the available material. There were some areas of improvement in some aspects such as time planning and work distribution because it was our first time working with this type of project so it was a little hard to know how to organise the work and set up a working schedule that fits all group members. 



