\section{Methods}
\subsection{Det här är också en underrubrik}
\subsubsection{Det här är underrubrikens rubrik}

\textbf{Arbetsfördelning, använde program (Trello, Slack) 
Gemensam databas så att alla kan jobba med allt samtidigt, eller när det passar.
Enligt kursen bestämde vi olika projektledare per vecka för hela projektet.
Varje vecka har vi möte för att bestämma planering och sätta upp uppgifter/mål.
Slutet av veckan har vi antingen haft möte själva eller med Cybercom(Jens) för att höra hur arbetet går.}
\bigskip 
%ger stort mellanrum \medskip ger lite mindre mellanrum \smallskip ännu mindre
%\paragraph{Här skriver man vad sin paragraph ska heta, det används mer då man vill dela upp sin text i olika delstycken typ om man ska förklara elektriska komponenter så blir varje delstycke en komponent }

The project was started by creating a common database to make working together easier for all group members. It was decided that the group would have a minimum of two meetings a week, at the beginning and the end of each week to review and discuss the work done so far and to put up goals/ tasks for the upcoming week. At the end of each week, the group would have a meeting with the supervisor at Cybercom, where he would check how the project is going, answer questions from the group members and give advise or help with the program software. Slack was used as a professional source of communication between all group members and so far it has made internal daily group contact simple and efficient. To organise the work and distribute the workload in a clear way between group members the Trello application together with the (with an influence of scrum )Scrum method to solve the tasks.. The group decided a case scenario to solve and with that the help of Scrum the scenario was broken into smaller tasks. In Trello the case scenario was documented together with the user cases in a backlog, and from there these user cases were broken down into smaller more concrete problems to solve. For each week the group \textit{organized?} tasks which would be distributed to all group members with \textit{avseende på} workload,  and time required to solve.
